\sffamily An EEG-based visual Brain-Computer Interface for gaze-free communication

### 2024-10-07 figures/bci/erp.tikz.tex
funding

\begin{tikzpicture}[trim axis left]
    \begin{axis}[
        width=\textwidth,
        height=0.6180\textwidth,
        scale only axis,
        xlabel={Time (ms)},
        ylabel={Potential ($\mu$V)},
        axis lines=middle,
	ylabel near ticks,
	xlabel near ticks,
	y label style={darkgray},
	x label style={darkgray},
        ymin=-5, ymax=10,
        xmin=-100, xmax=800,
        enlarge x limits=false,
        enlarge y limits=false,
        smooth,
        every axis plot/.append style={very thick, accent1}, % Set the line color to accent1
        ytick={-5,0,5}, % Y-ticks at -5, 0, 5
        xtick={200,400,600}, % X-ticks at 200, 400, 600, 800
        axis line style={darkgray}, % Set the axis line color to darkgray
        tick style={darkgray}, % Set the tick color to darkgray
        tick label style={darkgray} % Set the tick label color to darkgray
    ]
    % ERP waveform using cubic splines for smooth connection
    \addplot[
        smooth,
        tension=0.5
    ] coordinates {
        (-100, 0)  % Starting point
        (0, 0)     % Baseline
        (50, 0)    % Pre-P1
        (80, 2)    % P1
        (115, -3)  % N1
        (160, 3)   % P2
        (220, 1)   % N2
        (400, 7)   % P3
        (650, 1)   % LPP (Late Positive Potential)
        (800, 1)   % End point
    };

>>>>

\begin{tikzpicture}[trim axis left]
    \begin{axis}[
        width=\textwidth,
        height=0.6180\textwidth,
        xlabel={Time (ms)},
        ylabel={Potential ($\mu$V)},
        axis lines=middle,
        ymin=-5, ymax=10,
        xmin=-100, xmax=800,
        smooth,
        every axis plot/.append style={very thick, accent1}, % Set the line color to accent1
        ytick={-5,0,5}, % Y-ticks at -5, 0, 5
        xtick={200,400,600}, % X-ticks at 200, 400, 600, 800
      	ylabel near ticks,
      	xlabel near ticks,
        label style={darkgray, font=\footnotesize},
    ]
      % ERP waveform using cubic splines for smooth connection
      \addplot[
          smooth,
          tension=0.5
      ] coordinates {%
          (-100, 0)  % Starting point
          (0, 0)     % Baseline
          (50, 0)    % Pre-P1
          (80, 2)    % P1
          (115, -3)  % N1
          (160, 3)   % P2
          (220, 1)   % N2
          (400, 7)   % P3
          (650, 1)   % LPP (Late Positive Potential)
          (800, 1)   % End point
      };

### 2024-10-07 figures/wcble/smearing.tikz.tex
funding

\begin{tikzpicture}
    % First subplot (low jitter) positioned relative to center
    \begin{axis}[
        at={(-3cm,0cm)}, % Adjust position to the left, closer to the center
        anchor=center,
        width=7cm, height=6cm,
        xmin=20, xmax=80,
        ymin=-0.1, ymax=1.1,
        axis lines=none, % Remove axes
        title={Low Jitter}, % Add title
        title style={yshift=-10pt}, % Adjust title position to make it closer to the plot
        ]
        % Plot individual waveforms (low jitter) in darkgray
        \addplot[darkgray,domain=20:80,samples=100] {exp(-0.5*((x-50)/5)^2)};
        \addplot[darkgray,domain=20:80,samples=100] {exp(-0.5*((x-52)/5)^2)};
        \addplot[darkgray,domain=20:80,samples=100] {exp(-0.5*((x-48)/5)^2)};
        \addplot[darkgray,domain=20:80,samples=100] {exp(-0.5*((x-51)/5)^2)};
        \addplot[darkgray,domain=20:80,samples=100] {exp(-0.5*((x-49)/5)^2)};

@@

    % Second subplot (high jitter) positioned relative to center
    \begin{axis}[
        at={(3cm,0cm)}, % Adjust position to the right, closer to the center
        anchor=center,
        width=7cm, height=6cm,
        xmin=20, xmax=80,
        ymin=-0.1, ymax=1.1,
        axis lines=none, % Remove axes
        title={High Jitter}, % Add title
        title style={yshift=-10pt}, % Adjust title position to make it closer to the plot
        ]
        % Plot individual waveforms (high jitter) in darkgray
        \addplot[darkgray,domain=20:80,samples=100] {exp(-0.5*((x-45)/5)^2)};
        \addplot[darkgray,domain=20:80,samples=100] {exp(-0.5*((x-55)/5)^2)};
        \addplot[darkgray,domain=20:80,samples=100] {exp(-0.5*((x-40)/5)^2)};
        \addplot[darkgray,domain=20:80,samples=100] {exp(-0.5*((x-60)/5)^2)};
        \addplot[darkgray,domain=20:80,samples=100] {exp(-0.5*((x-50)/5)^2)};

@@

    % Unified legend positioned further below the center
    \node at (0,-5) {\begin{tikzpicture}
        \begin{axis}[
            hide axis,
            xmin=0, xmax=0, ymin=0, ymax=0,
            legend style={
	    	draw=none, legend columns=2, /tikz/every even column/.append
		style={column sep=2cm}
		}
            ]
            \addlegendimage{darkgray,thick}
            \addlegendentry{Waveforms}
            \addlegendimage{accent1,ultra thick}
            \addlegendentry{Average}
        \end{axis}
    \end{tikzpicture}};
\end{tikzpicture}
\vspace{-5cm}

>>>>

\sffamily
\sansmath
\begin{tikzpicture}   % First subplot (low jitter) positioned relative to center
    \begin{axis}[
        at={(0,0)}, % Adjust position to the left, closer to the center
        anchor=center,
        width=.45\textwidth, height=.309\textwidth,
        xmin=20, xmax=80,
        ymin=-0.1, ymax=1.1,
        axis lines=none, % Remove axes
        title={low jitter}, % Add title
        title style={yshift=-10pt, color=muteblack}, % Adjust title position to make it closer to the plot
        ]
        % Plot individual waveforms (low jitter) in darkgray
        \addplot[darkgray,domain=20:80,samples=100] {exp(-0.5*((x-50)/5)^2)};
        \addplot[darkgray,domain=20:80,samples=100] {exp(-0.5*((x-52)/5)^2)};
        \addplot[darkgray,domain=20:80,samples=100] {exp(-0.5*((x-48)/5)^2)};
        \addplot[darkgray,domain=20:80,samples=100] {exp(-0.5*((x-51)/5)^2)};
        \addplot[darkgray,domain=20:80,samples=100] {exp(-0.5*((x-49)/5)^2)};

@@

   % Second subplot (high jitter) positioned relative to center
   \begin{axis}[
      at={(0.55\textwidth,0)}, % Adjust position to the left, closer to the center
       anchor=center,
        width=.45\textwidth, height=.309\textwidth,
       xmin=20, xmax=80,
       ymin=-0.1, ymax=1.1,
       axis lines=none, % Remove axes
       title={high jitter}, % Add title
       title style={yshift=-10pt, color=muteblack}, % Adjust title position to make it closer to the plot
       ]
       % Plot individual waveforms (high jitter) in darkgray
       \addplot[darkgray,domain=20:80,samples=100] {exp(-0.5*((x-45)/5)^2)};
       \addplot[darkgray,domain=20:80,samples=100] {exp(-0.5*((x-55)/5)^2)};
       \addplot[darkgray,domain=20:80,samples=100] {exp(-0.5*((x-40)/5)^2)};
       \addplot[darkgray,domain=20:80,samples=100] {exp(-0.5*((x-60)/5)^2)};
       \addplot[darkgray,domain=20:80,samples=100] {exp(-0.5*((x-50)/5)^2)};

@@

   % Unified legend positioned further below the center
   \node[anchor=center] at (.3\textwidth,-.2\textwidth) {\begin{tikzpicture}
       \begin{axis}[
           hide axis,
           xmin=0, xmax=0, ymin=0, ymax=0,
           legend style={
	   	draw=none, legend columns=2, /tikz/every even column/.append
	 style={column sep=2cm}
	 }
           ]
           \addlegendimage{darkgray,thick}
           \addlegendentry{Waveforms}
           \addlegendimage{accent1,ultra thick}
           \addlegendentry{Average}
       \end{axis}
   \end{tikzpicture}};
\end{tikzpicture}
%\vspace{-5cm}
